\documentclass[10pt]{article}
\usepackage{titlesec}
\usepackage[margin=1in]{geometry}
\usepackage{titling}
\usepackage{blindtext}
\titleformat{\section}
{\huge\bfseries\lowercase}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}[runin]
{\bfseries}
{$\bullet$}
{0em}
{}[]
\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{}[:]

\renewcommand{\maketitle}{
	\begin{center}
	{\Large\textbf{Curriculum vitae}}\\
	\vspace{.62em}
	{\huge\bfseries\theauthor}\\
	\vspace{.62em}
	{\bfseries{mateja.vujsic@gmail.com| mateja.vujsic@prontomail.ch| +381 066 375 065}}
	\end{center}
}
\title{Curriculum vitae}
\author{\textbf{Mateja Vujsic}}
\begin{document}
\maketitle

\section{About me}
\subsection{\large{Name:}}
\textbf{\large{Mateja Vujsic}}
\subsection{\large{Date of birth:}}
\large{29. 4. 1998.}
\subsection{\large{Nationality:}}
\large{Serbian}
\subsection{\large{Languages:}}
\large{Serbian,English,German}
\subsection{\large{Education:}}
\subsubsection{First Grammary School, Kragujevac\hfill 2013. - 2017.}
\subsubsection{Faculty of Engineering Science, Kragujevac\hfill 2017. - 2022.}

\section{Personal profile}
\subsection{Email}
\textbf{mateja.vujsic@gmail.com} and \textbf{mateja.vujsic@protonmail.ch}
\subsection{Phone}
+381 066 375 065
\subsection{Github}
github.com/mvujsic

\section{Technical skills}
\subsection{Languages}
Python, C\#, Java, C , C++, Bash, Arduino, SQL , Node.JS, PHP
\subsection{Markup}
 jinja2, XAML, HTML, \LaTeX,Pug
\subsection{Tools}
Linux, Git, MySQL, SQLite, Pycharm, Atom, VisualStudio, MPLab IDE, SolidWorks,  Microsoft Office,  LibreOffice

\section{experience}
\subsection{\large{Tim-ing Center D.O.O}}
\subsubsection{Date}
03.2021.-06.2021.
\subsubsection{Position}
C\# Junior Developer and PLC ladder logic engineer
\subsubsection{Worked on}
\textbf{C\# WPF} main program working on Windows Embedded, handling a depth and color matrix streamed by Kinect v1 and v2 cameras with Kinect SDK;\\
Ladder logic program development, working mainly with \textbf{FATEK and OMRON} equipment, FATEK and Modbus comunication protocol and WinProladder IDE.\\
\textbf{MySQL} database administration.\\

\subsection{\large{Astora IT Remote Consulting Company - remote UpWork agency}}
\subsubsection{Date}
10.2021.-11.2022.
\subsubsection{Position}
Junior Python Backend Developer - remote
\subsubsection{Worked on}
Majority of work include data scraping and analytics, developing \textbf{GUI application} and web-application with user inputs (mostly in \textbf{ Flask/Django/Plotly Dash/Quart} ), reverse engineering
https sites with login and captcha secured (python libs \textbf{Requests, Selenium, TwoCaptcha solver, HCaptcha solver}) and extraction of requested cilent data - python scripting for job automation. Using \textbf{asyncio} module on daily bases.
\\ Using tools like \textbf{Linux, Git,  PyCharm, VS Code} on daily basis.  \\
Familiar with async programming concepts, and legacy codebase.
\textbf{MySQL , SQLite,  Postgres} database administration with advance queries and ORM modules.\\
\textbf{Heroku and NGINX} deployment process with gunicorn and uvicorn - reverse proxy sites.\\
\textbf{Facebook Marketing API and Google Analytics API} scripts .\\

\subsection{\large{Red-Black Tree - Belgrade}}
\subsubsection{Date}
11. 2022. -  now
\subsubsection{Position}
Junior Python Backend Developer - remote
\subsubsection{Projects}
\subsection{{\textbf{IMentor} 11.2022 - 05.2023}}
\textbf{Backend}-majority of work-opening endpoint in Flask framework,
Marshmallow-for validating schemas (loading/dumping),
RQ-used for background task,
Flask-SQLAlchemy with advance queries with relationship loading technics,
Unit Testing,
Flask-Alembic,
Postgres,
Integrations-Twilio/Tableau/SF,
Vagrant as local environment - basics,
Git-advance and complex workflow,
Jira/Confluence,
Harvest-for tracking work hours
\subsection{{\textbf{Problemshared} 05.2023 - now}}
\textbf{Backend} Flask framework,
Marshmallow-for validating schemas (loading/dumping),
RQ-used for background task,
SQLAlchemy with advance queries with relationship loading technics,
Alembic,
Postgres,
Integrations-Auth0/Mailgun/Zendesk/Semble/DBT,
Docker as local environment,
Terraform-basics,
AWS-mainly searching Logs Insight
Git-advance and complex workflow,
Jira/Confluence,
Harvest-for tracking work hours

\subsection{\textbf{Student projects}}
\subsubsection{Projects}
Database designs for systems such as shop,company...\\
Web scraping and data mining\\
Arduino (Uno,Mega,Nano), Esp8266, Esp32, RaspberryPi SenseHat programming\\
DIY Smart home appliance with ESP8266 \\
C{\#} WPF, Java JFRAME, Python PYQT5 project connected to local database\\
\subsubsection{Python}
Celery project-alternative for RQ, find it on my Github

\section{Hobby}
\subsection{Programming microcontrollers}
\subsection{3D modeling in SOLIDWORKS}
\subsection{Linux enthusiast}

\end{document}